Domain-agnostic Outlier Ranking Algorithms (DORA)---A Configurable Pipeline for Facilitating Outlier Detection in Scientific Datasets

### 2021-12-06 publications/iaai21/dora_outlier_detection_iaai.tex
Fix typo in manuscript.

\section{Datasets}
We constructed three datasets to evaluate the utility of DORA and 
algorithm performance for a variety of scientific domains
 (astrophysics, planetary science, and Earth science). We also included a 
 benchmark dataset that uses MNIST and Fashion-MNIST. Table \ref{tab:datasets}
 summarizes the number of unlabeled samples used for training evaluation for
 each dataset. We describe each dataset in detail below.

@@

For the astrophysics dataset (Figure~\ref{fig:des_results}), DEMUD was omitted due to computational time 
and LRX was omitted as it applies only to image data.  Of the remaining methods, 
PCA achieved the highest precision, following by RX.  Negative sampling 
performs well initially before its performance drops off.  The PAE finds the most outliers 
overall.

>>>>

\section{Datasets}
We constructed three datasets to evaluate the utility of DORA and 
algorithm performance for a variety of scientific domains
 (astrophysics, planetary science, and Earth science). We also included a 
 benchmark dataset that uses MNIST and Fashion-MNIST. Table \ref{tab:datasets}
 summarizes the number of unlabeled samples used for training and evaluation for
 each dataset. We describe each dataset in detail below.

@@

For the astrophysics dataset (Figure~\ref{fig:des_results}), DEMUD was omitted due to computational time 
and LRX was omitted as it applies only to image data.  Of the remaining methods, 
PCA achieved the highest precision, followed by RX.  Negative sampling 
performs well initially before its performance drops off.  The PAE finds the most outliers 
overall.
